Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-30 draft/paper1_v12.tex
New draft version

@@

    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
    relations using the $k$-corrected $g-r$ color. 
    Both samples follow the same tight ``red-sequence'' with little contamination 
    from the ``blue cloud''.
    At fixed \mtot{}, we see little offset in color distributions of the two 
    samples, suggesting that both samples consist of quiescent galaxies with 
    similar average stellar population properties.  
    This is consistent with previous result that suggests the average stellar 
    population of massive central galaxy does not depend on \mhalo{} 
    (e.g.\ \citealt{Park2007}).  
    In this work, we focus on the \mstar{} range of $11.6 \le$\logmtot{}$\le 11.9$, 
    where both samples have acceptable completeness, and their \mtot{} distributions 
    greatly overlap (see the normalized distributions of \mtot{} in the bottom-left 
    panel of Fig~\ref{fig:sample_stats}). 
    As for the \minn{} distributions, the two samples overlap the most within 
    $11.2 \le$\logmtot{}$\le 11.6$, but now they show quite different
    distributions (bottom-right figure).

    The redshift distributions also show small difference
    (upper-right panel) even in the high-\mtot{} bin, where the redshift distribution 
    of the \nbcg{} sample skews toward higher-$z$ end due to the contribution of BOSS 
    spec-$z$.

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_sample_stats}
      \caption{
          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
          (red circle; detaield format is the same with the right panel of 
          Fig~\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
          mass bins.
          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
          $0.3 \leq z \leq 0.5$ (stepped histogram). 
          The vertical lines in both top-left and bottom-left figures highlight the 
          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
          the \mtot{}-matched samples.~~
          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
          Here the vertical lines highlight the 
          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
      }
      \label{fig:sample_stats}
  \end{figure}
%% ------------------------------------------------------------------------------------ %%

>>>>

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_sample_stats}
      \caption{
          \textbf{Top-left}: The \logmtot{}-$(g-r)$ rest-frame color relation for the 
          HSC massive galaxies.
          We $k$-correct the color using the \texttt{iSEDFit} fitting results.
          Massive galaxies form a ``red-sequence'' on this figure, and there is 
          little contamination from blue object at high-mass end.~~          
          \textbf{Top-right}: the redshift distribution of the massive galaxies. 
          The filled and empty histograms are for the \logmtot{}$>11.6$ and 
          \logmtot{}$>11.2$ galaxies.
          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
          \textbf{Bottom-left}: the distributions of \mtot{} of massive galaxies in 
          this sample. 
          Filled histogram shows the distribution for $0.3 < z < 0.5$ galaxies 
          used in this work. 
          And the empty histogram shows the distribution for the whole $z>0.2$ sample
          as comparison.~~
          \textbf{Bottom-right}: the distributions of \minn{} in similar format. 
      }
      \label{fig:sample_stats}
  \end{figure}
%% ------------------------------------------------------------------------------------ %%

@@

    Here we show the basic statistics of the massive galaxies used in this work.
    On the top-left panel of Fig~\ref{fig:sample_stats}, we show the \mtot{}-color 
    relation using the $k$-corrected rest-frame $(g-r)$ color. 
    These massive galaxies form a clear ``red-sequence'' with little contamination 
    from the ``blue cloud'' at the very high-mass end.

    In the rest of Fig~\ref{fig:sample_stats}, we also show the distributions of 
    redshift, \mtot{}, and \minn{}.
    In this work, we focus on the massive galaxies with \logmtot{}$>11.6$ at 
    $0.3 < z < 0.5$ where the sample is fairly complete in \mtot{}.

    % TODO: Move to Paper II
    % At fixed \mtot{}, we see little offset in color distributions of the two 
    % samples, suggesting that both samples consist of quiescent galaxies with 
    % similar average stellar population properties.  
    % This is consistent with previous result that suggests the average stellar 
    % population of massive central galaxy does not depend on \mhalo{} 
    % (e.g.\ \citealt{Park2007}).  
    % In this work, we focus on the \mstar{} range of $11.6 \le$\logmtot{}$\le 11.9$, 
    % where both samples have acceptable completeness, and their \mtot{} distributions 
    % greatly overlap (see the normalized distributions of \mtot{} in the bottom-left 
    % panel of Fig~\ref{fig:sample_stats}). 
    % As for the \minn{} distributions, the two samples overlap the most within 
    % $11.2 \le$\logmtot{}$\le 11.6$, but now they show quite different
    % distributions (bottom-right figure).

    % The redshift distributions also show small difference
    % (upper-right panel) even in the high-\mtot{} bin, where the redshift distribution 
    % of the \nbcg{} sample skews toward higher-$z$ end due to the contribution of BOSS 
    % spec-$z$.
